### 2015-06-18 chapters/ipa_meets_unicode.tex
different organisation of IPA homoglyph section

% this has to be revised: there are two issues: homoglyphs and alternative 
encoding options. that is not necessarily the same. Also include minor group break 
vs. dental click problem. and stress vs. ejective?

>>>>

Reversely, there are a few cases in which the IPA distinguishes different
concepts, but the visual marking proposed by the IPA look very much alike. Such
cases are thus homoglyphs in the IPA itself, which of course need different
encodings.

   \item The dental click <ǀ> and the indication of a minor group break <|>
           (proposed to be used for separating feet) look almost the same in
           most fonts. For a proper encoding, the \textsc{latin letter dental
           click} at \uni{01C0} and the \textsc{vertical line }at \uni{007C} 
           should be strictly distinguished.
   \item Similarly, the alveolar lateral click <ǁ>	should be encoded with a
           \textsc{latin letter lateral click} at \uni{01C1}, different from <‖>, 
           which according to the IPA is a major group break (by intonation), to be
           encoded by \textsc{double vertical line} at \uni{2016}.
   \item The marking of primary stress < ˈ > looks like an apostrophe, and
           is often typed with the same symbol as the ejective < ʼ >. For a
           proper encoding, these two symbols should be typed as 
           \textsc{modifier letter vertical line} at \uni{02C8} and
           \textsc{modifier letter apostrophe} at \uni{02BC}, respectively.

% ==========================
\section{Pitfall: Multiple options in IPA}
\label{pitfall-multiple-options-ipa}     
% ==========================
